Elastic Scattering in General Relativistic Ray Tracing for Neutrinos

### 2017-02-13 paper.tex
Reorder authors
Add acknowledgements

>>>>

\subsubsection*{Acknowledgements}
This research is supported in part by the Joint Institute for Nuclear
Astrophysics---Center for the Evolution of the Elements (JINA-CEE)
and the National Science Fondation under grant numbers X. \todo{grant nos?}
We thank Sherwood Richers for providing his neutrino transport code
\lstinline{Sedonu}~\footnote{\url{https://bitbucket.org/srichers/sedonu}}
for comparisons.
We thank Luke Roberts and Yonglin Zhu for helpful discussions.
